\documentclass{article}

%-------------------------------------------------------------------------------
%                Packages
%-------------------------------------------------------------------------------

% Needed to make fixed length table
\usepackage{array}
% Needed to configure page layout
\usepackage{geometry}
% Needed to make header & footer
\usepackage{fancyhdr}
% Needed to manage colors
\usepackage{xcolor}
% Needed to make the header
\usepackage{tikz}
\usepackage[absolute, overlay]{textpos} % The most useful latex package
% Needed to make hyperlinks
\usepackage[hidelinks]{hyperref}
% Needed to use icons from font-awesome
\usepackage{fontawesome}


%-------------------------------------------------------------------------------
%                Parameters
%-------------------------------------------------------------------------------

% Page Margins
\geometry {
	left = 0.5cm,
	top = 1cm,
	right = 1.2cm,
	bottom = 2cm
}

% Colors
\definecolor{main_color}    {RGB} { 0,  0,  130}
\definecolor{line_color}    {RGB} {160, 160, 255}
\definecolor{dash_color}    {RGB} {100, 100, 255}

% Makes the footer
\pagestyle{fancyplain}
\fancyhf{}
% Removes the header line
\renewcommand{\headrulewidth}{0pt}
\lfoot{ \hskip 10pt  \bf \today}
\rfoot{ \bf \thepage}

%-------------------------------------------------------------------------------
%                New commands
%-------------------------------------------------------------------------------

% Defining special columns used in the table
\newcolumntype{L}{>{\color{black}\raggedleft}p{0.14\textwidth}}
\newcolumntype{D}{>{\color{black}}p{0.83\textwidth}}

% Makes a single entry in a section
\newcommand{\mainitem}[3] {
    \textbf{#1}  \newline #2 \vskip5pt  \textit{#3} 
    \vspace{6pt}    % Space between each entry
}

% Makes the tables after each section
\newenvironment{cvtable} {
	\hspace{-20pt} \begin{tabular}{L!{\color{line_color}\vrule width 1pt}D} % Removes the unexplained large gap to the left
} 
{\end{tabular}}

% Used when making a list
\newenvironment{cvitemize} {
    \textit
	\normalfont
	\begin{itemize}
} 
{\end{itemize} \vspace{-15pt}} % Removes the unexplained large gap after each list

%-------------------------------------------------------------------------------
%                Renew commands
%-------------------------------------------------------------------------------

% Changing the default font to Gyre Adventor
\renewcommand{\familydefault}{qag}

% Changing the default section command
\renewcommand{\section}[1] {
    \vspace{15pt}   % Size of the gap between each section
	{\color{main_color} \Large \textbf {#1}}
	{\color{line_color} \vskip-5pt \rule{\linewidth}{0.5mm}\hfill\vskip-11pt\rule{\linewidth}{0.2pt}}
	\vskip10pt  % Size of the gap after each section title
}

% Changes the default list item from a dot to a dash
\renewcommand{\labelitemi}{\color{dash_color}\raisebox{1.2pt}{$-$}}

%-------------------------------------------------------------------------------
%                The Document
%-------------------------------------------------------------------------------


\begin{document}
	\begin{tikzpicture}[absolute, remember picture, overlay]
		\node[rectangle, fill = main_color, anchor = north west, minimum width = \paperwidth+1cm, minimum height = 3.3cm] at (current page.north west) {};
	\end{tikzpicture}
	
	\begin{textblock}{16.1}(0, 0.2)
		\color{white}
		\begin{center}
			\textbf{{\Huge Mihailo Grbi\' c}} 
			\\[6pt]
			{\Large  Electrical and Computer Engineering Student} 
			\\[13pt]
			\begin{tabular}{c | c | c | c}
				{\faEnvelope} 
				\href{mailto:mihailogrbic99@gmail.com}{mihailogrbic99@gmail.com} 
				    \hspace{5.5pt}
				    & 
				    \hspace{5.5pt}
				\raisebox{-1.2pt}{\Large\faMobilePhone}
				+381 62 795895 
					\hspace{5.5pt}
				    & 
				    \hspace{5.5pt}
				\raisebox{0.7pt}{\large\faLinkedin}\hspace{2pt}
				\href{https://rs.linkedin.com/in/mihailo-grbić-891953152}{Mihailo Grbi\' c}
				    \hspace{5.5pt}
					&
                    \hspace{5.5pt}
                {\large\faGithub}
				\href{https://github.com/MihailoGrbic}{MihailoGrbic}
			\end{tabular}
		\end{center}
	\end{textblock}
    
    
    % Move the first section down so it doesn't overlap with the title
    \vspace{60pt}
    
    
    \section{Education}
    	\begin{cvtable}
    		2018 - \textit{present} & 
    			\mainitem
    				{Belgrade University, Faculty of Electrical Engineering}
    				{Belgrade, Serbia} 
    				{
    				Second-year student at the Electrical and Computer Engineering program (module Signals and Systems). Expected graduation date July 2022. GPA 9.79/10
    				} 
    		\\
    		2014 - 2018 & 
    			\mainitem
    				{Mathematical Grammar School}
    				{Belgrade, Serbia} 
    				{
    					 Honors class of top twenty students based on their entrance exam score and their accomplishments on competitions. GPA 4.85/5
    				} 
    	\end{cvtable}
    
    
    \section{Work Experience}
    	\begin{cvtable}
    	    \hspace{5pt} July 2019 - Oct. 2019  & 
    			\mainitem
    			    {Microsoft Development Center Serbia, Cognition Serbia}
    				{Software Engineer Intern} {
    				    Was tasked with analyzing the viability of a new, confidential feature.
    					Read around 20 science papers, filtered out 3 methods that were the most promising, implemented them, and performed extensive analysis of their performance and viability for commercial use. The methods were implemented using \textbf{Python} and \textbf{Pytorch}, and cover the topics of \textbf{geometric computer vision}, \textbf{automatic differentiation}, and \textbf{machine learning}.
    				}
    	\end{cvtable}
    
    \section{Projects}
    	\begin{cvtable}
    	    \hspace{5pt} July 2018 - Dec. 2018 & 
    			\mainitem
    			    {Pipelined FPGA architecture for filtering images with linear and adaptive median filter}
    			    {Petnica Science Center} 
    			    {
    			        Designed and implemented a pipelined \textbf{FPGA} architecture which applies linear and adaptive median filter on images, with focus on fast execution and minimal load on system memory bandwidth. The implemented architecture requires at least 9 times less system memory readings compared to a traditional, general-purpose processor implementation of these algorithms. Wrote a research paper which was featured at 2018. Annual Petnica Conference and was published in 2018. edition of the Petnica Science Journal.
                    } 
    	    \\
    		\hspace{5pt} July 2017 - Dec. 2017 & 
    			\mainitem
    			    {Training dataset enlargement using Generative Adversarial Networks}
    			    {Petnica Science Center} 
    			    {
    			        Tested the viability of using \textbf{Generative Adversarial Networks (GAN)} to enlarge training datasets for classification machine learning problems. Implemented a \textbf{CNN} classifier for the Street View House Numbers problem, and a \textbf{Deep Convolutional Generative Adversarial Network (DCGAN)}, using \textbf{Python} and \textbf{Tensorflow}. Wrote a research paper which was featured at 2017. Annual Petnica Conference and was published in 2017. edition of the Petnica Science Journal.
                    }
    	\end{cvtable}
    	
    \newpage

    \section{Projects}
    	\begin{cvtable}
    		\hspace{5pt} May 2017 - June 2017 & 
    			\mainitem
    			    {Digital Circuit Simulation}
    			    {Mathematical Grammar School} 
    			    {
                        The goal of the project was to make a digital circuit simulator (inspired by Logisim), to implement it using \textbf{Object Oriented Programming} and to document the code fully. All basic logic gates were implemented, as well as wires, transistors, logical pins, clocks, and displays. Was done in a team of 3 people.
                    }
    	\end{cvtable}

    \section{Extracurricular Activities}
        \begin{cvtable}
    	    Sept. 2016 - Sept. 2018 & 
    		    \mainitem
    				{Sekcija Primenjene Fizike i Elektronike Matemati\v cke gimnazije (PFEMG)}
    				{Founder and Head} 
    				{   
    				    \vspace{-16pt}
    				    \begin{cvitemize} \itemsep0em
    				        \item Founded and lead a student club of Applied Physics and Electronics at Mathematical Grammar School. 
    				        \item Treated it as a small startup, building it up from an empty, unused classroom to a well-respected club with over 20 members.
    					    \item Mentored student projects.
                            \item Held lectures and workshops on a wide range of subjects.
                            \item Managed the club's equipment and finances.
                            \item Organized the club's participation and its displays at multiple science festivals, including Belgrade Science Festival and MakerFaire Vienna.
                            \item Contacted potential sponsors and raised over \$5k worth of funds and equipment for the club.
    				    \end{cvitemize}
                    }   
            \\
    		\hspace{5pt} Dec. 2015 - Nov. 2018 &
    			\mainitem
    				{Petnica Science Center, Department of Applied Physics and Electronics}
    				{Attendee} 
    				{
    				    Attended 15 weeks (in total) worth of seminars which consist of lectures and workshops on the subjects of electronics, robotics, control systems, computer vision, and machine learning. Worked on 3 summer research projects and wrote 2 research papers.
    				}
            \\
    		\vspace{-3pt}May 2018 - \textit{present} & 
    			\mainitem
    			    {\vspace{-15pt}}
    				{Junior Assistant} {
    					Hold lectures and workshops on the subjects of programming, computer vision, and machine learning. Mentor student projects. (4 weeks per year) 
    				}
            \\
            Aug. 2019 & 
    		    \mainitem
    				{Petnica Summer Institute of Machine Learning (PSIML)}
    				{Attendee} 
    				{   
    				    Attended a 10-day machine learning course organized by Microsoft Development Center Serbia. Implemented a neural network for \textbf{semantic segmentation} of a hand from depth images, as part of a small team project.
                    }   
            \\
            Dec. 2015 - Dec. 2018 & 
                \mainitem
    				{Computer Science Week at Mathematical Grammar School (CSNedelja)}
    				{Attendee}
    				{
    				    Attended the annual, week-long seminar consisting of lectures and workshops which cover a wide range of areas in computer science, held to a select group of students.
    				}
            \\
            \vspace{-3pt}Dec. 2018 - \textit{present} & 
                \mainitem
    				{\vspace{-15pt}}
    				{Lecturer}
    				{
    					Hold lectures and workshops on the subjects of computer vision and machine learning at the annual seminar.
    				}
    	\end{cvtable}
    

            
    \newpage
    
    \section{\textbf{Honours \& Awards}}
    	\begin{cvtable}
    	    2016 - \textit{present} &
     	        \mainitem
     	            {Scholarship for exceptionally talented students}
     	            {Government of Serbia, Ministry of Education}
     	            {
                        Awarded by the Serbian Ministry of Education, Sciences, and Technological Development for maintained academic success and exceptional achievements at national competitions and extracurricular activities.
    				}
    		\\
            2015 - 2017 &
    			\mainitem
    			    {Serbian High School Competition Awards}
    			    {Government of Serbia, Ministry of education} 
    			    {
    				    One 2\textsuperscript{nd} and two 3\textsuperscript{rd} awards at national physics competitions. One 3\textsuperscript{rd} award and two honorable mentions at national programming competitions.
    			    } 
    		\\
     		July 2018 &
     	        \mainitem
     	            {RetailTech Hackathon 3rd place}
     	            {ICT Hub, Delhaize Serbia}
     	            {
    					A 48-hour hackathon with the challenge of improving the in-store digital experience of Delhaize markets.  Was part of a 4 member team. We made an Android app MaxiGO which won 3rd place in a competition of 11 teams.
    				}
    		\\
     		April 2017 &
     	        \mainitem
     	            {CoderDojo Pan\v cevo Robotics Hackathon 1st place}
     	            {Coder Dojo Pan\v cevo} 
     	            {
     	                A 48-hour hackathon aimed at high school students with the challenge of making a creative and useful robot.
    				    Was part of a 3 member team. We made a robot SoilBuggy which won 1st place in a competition of 7 teams.
    				} 
    		\\
            December 2016 &
     	        \mainitem
     	            {Decembarac Debate Competiton, Best Individual Speaker}
     	            {Open Communication, Faculty of Law} 
     	            {
    					An annual, team, debate competition played by British parliament rules. 
    					Awarded the Best individual speaker award out of 122 participants.
    				}
    	\end{cvtable}
    	
    \section{\textbf{Courses \& Certifications}}
        \begin{cvtable}
     		May 2019 &
     	        \mainitem
     	            {Stanford Machine Learning Course}
     	            {Coursera} 
     	            {
     	            \vspace{-20pt}
    				} 
    		\\
     		Oct. 2018 &
     	        \mainitem
     	            {VHDL and FPGA Development Online Course}
     	            {Udemy}
     	            {
     	            \vspace{-20pt}
    				}
    	\end{cvtable}
\end{document}